\item 
Julien Aubert-Béduchaud, \textbf{Florian Boudin}, Béatrice Daille, Richard Dufour.
2025.
\href{https://aclanthology.org/2025.coling-main.327.pdf}{ACL-rlg : A Dataset for Reading List Generation}.
\textit{International Conference on Computational Linguistics (COLING)}.
\label{aubert-beduchaud-etal-2025-acl}

\item 
Maël Houbre, \textbf{Florian Boudin}, Béatrice Daille, Akiko Aizawa.
2024.
\href{https://arxiv.org/pdf/2411.03039}{Self-Compositional Data Augmentation for Scientific Keyphrase Generation}.
\textit{Joint Conference on Digital Libraries (JCDL)}.
\label{houbre-etal-2024-self}

\item
\textbf{Florian Boudin}, Akiko Aizawa.
2024.
\href{https://aclanthology.org/2024.findings-emnlp.33.pdf}{Unsupervised Domain Adaptation for Keyphrase Generation using Citation Contexts}.
\textit{In Findings of the Conference on Empirical Methods in Natural Language Processing (EMNLP)}.
\label{boudin-aizawa-2024-unsupervised}

\item 
Léane Jourdan, \textbf{Florian Boudin}, Nicolas Hernandez, Richard Dufour.
2024.
\href{https://aclanthology.org/2024.lrec-main.257.pdf}{CASIMIR: A Corpus of Scientific Articles enhanced with Multiple Author-Integrated Revisions}.
\textit{Joint International Conference on Computational Linguistics, Language Resources and Evaluation (LREC-COLING)}.
\label{jourdan-etal-2024-casimir}

\item
Amir Hazem, Mérieme Bouhandi, \textbf{Florian Boudin}, Beatrice Daille.
2022.
\href{https://aclanthology.org/2022.lrec-1.68.pdf}{Cross-lingual and Cross-domain Transfer Learning for Automatic Term Extraction from Low Resource Data}.
\textit{Language Resources and Evaluation Conference (LREC)}.
\label{hazem-etal-2022-cross}

\item
Rui Meng, Debanjan Mahata, \textbf{Florian Boudin}.
2022.
\href{https://link.springer.com/chapter/10.1007/978-3-030-99739-7_73}{From Fundamentals to Recent Advances: A Tutorial on Keyphrasification}.
\textit{European Conference on Information Retrieval (ECIR)}.
\label{meng-etal-2022-fundamentals}

\item 
\textbf{Florian Boudin}, Ygor Gallina.
2021.
\href{https://www.aclweb.org/anthology/2021.naacl-main.330.pdf}{Redefining Absent Keyphrases and their Effect on Retrieval Effectiveness}.
\textit{Conference of the North American Chapter of the Association for Computational Linguistics (NAACL)}.
\label{boudin-gallina-2021-redefining}

\item
\textbf{Florian Boudin}.
2021.
\href{https://arxiv.org/pdf/2108.07571.pdf}{ACM-CR: A Manually Annotated Test Collection for Citation Recommendation}.
\textit{Joint Conference on Digital Libraries (JCDL)}.
\label{boudin-2021-acm}

\item
\textbf{Florian Boudin}, Ygor Gallina, Akiko Aizawa.
2020.
\href{https://aclanthology.org/2020.acl-main.105.pdf}{Keyphrase Generation for Scientific Document Retrieval}.
\textit{Association for Computational Linguistics (ACL)}.
\label{boudin-etal-2020-keyphrase}

\item
Ygor Gallina, \textbf{Florian Boudin}, Béatrice Daille.
2020.
\href{https://dl.acm.org/doi/10.1145/3383583.3398517}{Large-Scale Evaluation of Keyphrase Extraction Models}.
\textit{Joint Conference on Digital Libraries (JCDL)}.
\label{gallina-etal-2020-large}

\item
\textbf{Florian Boudin}, Béatrice Daille, Evelyne Jacquey, Jian-Yun Nie.
2020.
\href{http://ceur-ws.org/Vol-2621/CIRCLE20_27.pdf}{The DELICES Project: Indexing Scientific Literature Through Semantic Expansion}.
\textit{Joint Conference of the Information Retrieval Communities in Europe (CIRCLE)}.
\label{boudin-etal-2020-delices}

\item
Kenichi Iwatsuki, \textbf{Florian Boudin}, Akiko Aizawa.
2020.
\href{https://aclanthology.org/2020.lrec-1.212.pdf}{An Evaluation Dataset for Identifying Communicative Functions of Sentences in English Scholarly Papers}.
\textit{Language Resources and Evaluation Conference (LREC)}.
\label{iwatsuki-etal-2020-evaluation}

\item 
Ygor Gallina, \textbf{Florian Boudin}, Béatrice Daille.
2019.
\href{https://aclanthology.org/W19-8617.pdf}{KPTimes: A Large-Scale Dataset for Keyphrase Generation on News Documents}.
\textit{International Conference on Natural Language Generation (INLG)}.
\label{gallina-etal-2019-kptimes}

\item
\textbf{Florian Boudin}.
2018.
\href{https://aclanthology.org/N18-2105.pdf}{Unsupervised Keyphrase Extraction with Multipartite Graphs}.
\textit{Conference of the North American Chapter of the Association for Computational Linguistics (NAACL)}.

\item 
\textbf{Florian Boudin}.
2016.
\href{https://aclanthology.org/C16-2015.pdf}{\texttt{pke}: an open source python-based keyphrase extraction toolkit}.
\textit{International Conference on Computational Linguistics (COLING)}.
\label{boudin-2018-unsupervised}

\item 
Adrien Bougouin, \textbf{Florian Boudin}, Béatrice Daille.
2016.
\href{https://aclanthology.org/C16-1277.pdf}{Keyphrase Annotation with Graph Co-Ranking}.
\textit{International Conference on Computational Linguistics (COLING)}.
\label{bougouin-etal-2016-keyphrase}

\item 
Adrien Bougouin, Sabine Barreaux, Laurent Romary, \textbf{Florian Boudin}, Béatrice Daille.
2016.
\href{https://aclanthology.org/L16-1304.pdf}{TermITH-Eval: a French Standard-Based Resource for Keyphrase Extraction Evaluation}.
\textit{Language Resources and Evaluation Conference (LREC)}.
\label{bougouin-etal-2016-termith}

\item 
\textbf{Florian Boudin}, Hugo Mougard, Benoit Favre.
2015.
\href{https://aclanthology.org/D15-1220.pdf}{Concept-based Summarization using Integer Linear Programming: From Concept Pruning to Multiple Optimal Solutions}.
\textit{Conference on Empirical Methods in Natural Language Processing (EMNLP)}.
\label{boudin-etal-2015-concept}

\item 
Ophélie Lacroix, Denis Béchet, \textbf{Florian Boudin}.
2014.
\href{https://hal.archives-ouvertes.fr/hal-01004007/file/CICLing2014.pdf}{Label Pre-annotation for Building Non-projective Dependency Treebanks for French}.
\textit{Conference on Intelligent Text Processing and Computational Linguistics (CICLing)}.
\label{lacroix-etal-2014-label}

\item
Adrien Bougouin, \textbf{Florian Boudin}, Béatrice Daille.
2013.
\href{https://aclanthology.org/I13-1062.pdf}{TopicRank: Graph-Based Topic Ranking for Keyphrase Extraction}.
\textit{International Joint Conference on Natural Language Processing (IJCNLP)}.
\label{bougouin-etal-2013-topicrank}

\item 
\textbf{Florian Boudin}.
2013.
\href{https://aclanthology.org/I13-1102.pdf}{A Comparison of Centrality Measures for Graph-Based Keyphrase Extraction}.
\textit{International Joint Conference on Natural Language Processing (IJCNLP)}.
\label{boudin-2013-comparison}

\item
\textbf{Florian Boudin}, Emmanuel Morin.
2013.
\href{https://aclanthology.org/N13-1030.pdf}{Keyphrase Extraction for N-best Reranking in Multi-Sentence Compression}.
\textit{Conference of the North American Chapter of the Association for Computational Linguistics (NAACL)}.
\label{boudin-morin-2013-keyphrase}

\item 
\textbf{Florian Boudin}, Jian-Yun Nie, Martin Dawes.
2012.
\href{https://link.springer.com/chapter/10.1007/978-3-642-28997-2_46}{Using a Medical Thesaurus to Predict Query Difficulty}.
\textit{European Conference on Information Retrieval (ECIR)}.
\label{boudin-etal-2012-medical}

\item 
\textbf{Florian Boudin}, Stéphane Huet, Juan-Manuel Torres-Moreno.
2011.
\href{http://polibits.gelbukh.com/2011_43/43_16.pdf}{A Graph-based Approach to Cross-language Multi-document Summarization}.
\textit{Conference on Intelligent Text Processing and Computational Linguistics (CICLing)}.
\label{boudin-etal-2011-graph}

\item 
\textbf{Florian Boudin}, Jian-Yun Nie, Martin Dawes.
2010.
\href{https://aclanthology.org/D10-1011.pdf}{Positional Language Models for Clinical Information Retrieval}.
\textit{Conference on Empirical Methods in Natural Language Processing (EMNLP)}.
\label{boudin-etal-2010-positional}

\item 
\textbf{Florian Boudin}, Jian-Yun Nie, Martin Dawes.
2010.
\href{https://aclanthology.org/N10-1124.pdf}{Clinical Information Retrieval using Document and PICO Structure}.
\textit{Conference of the North American Chapter of the Association for Computational Linguistics (NAACL)}.
\label{boudin-etal-2010-clinical}

\item 
\textbf{Florian Boudin}, Lixin Shi, Jian-Yun Nie.
2010.
\href{https://link.springer.com/chapter/10.1007/978-3-642-12275-0_8}{Improving Medical Information Retrieval with PICO Element Detection}.
\textit{European Conference on Information Retrieval (ECIR)}.
\label{boudin-etal-2010-improving}

\item 
\textbf{Florian Boudin}, Marc El-Bèze, Juan-Manuel Torres-Moreno.
2008.
\href{https://aclanthology.org/C08-2006.pdf}{A Scalable MMR Approach to Sentence Scoring for Multi-Document Update Summarization}.
\textit{International Conference on Computational Linguistics (COLING)}.
\label{boudin-etal-2008-scalable}

\item 
\textbf{Florian Boudin}, Juan Torres-Moreno, Marc El-Bèze.
2008.
\href{https://link.springer.com/chapter/10.1007/978-3-540-78135-6_28}{Mixing Statistical and Symbolic Approaches for Chemical Names Recognition}.
\textit{Conference on Intelligent Text Processing and Computational Linguistics (CICLing)}.
\label{boudin-etal-2008-mixing}

\item 
\textbf{Florian Boudin}, Juan-Manuel Torres-Moreno, Patricia Velázquez-Morales.
2008.
\href{https://link.springer.com/content/pdf/10.1007/978-3-540-85287-2_9}{An Efficient Statistical Approach for Automatic Organic Chemistry Summarization}.
\textit{International Conference on Natural Language Processing (GoTAL)}.
\label{boudin-etal-2008-efficient}

\item 
\textbf{Florian Boudin}, Juan-Manuel Torres-Moreno.
2007.
\href{https://hal.science/hal-01313205}{A Cosine Maximization Minimization approach for User Oriented Multi-Document Update Summarization}.
\textit{Recent Advances in Natural Language Processing (RANLP)}.
\label{boudin-torres-moreno-2007-cosine}

\item 
\textbf{Florian Boudin}, Juan Torres Moreno.
2007.
\href{https://link.springer.com/chapter/10.1007/978-3-540-70939-8_49}{NEO-CORTEX: A Performant User-Oriented Multi-Document Summarization System}.
\textit{Conference on Intelligent Text Processing and Computational Linguistics (CICLing)}.
\label{boudin-torres-moreno-2007-neo}