\item
Léane Jourdan, Nicolas Hernandez, Richard Dufour, \textbf{Florian Boudin}, Akiko Aizawa.
2025.
\href{https://arxiv.org/abs/2501.05222}{ParaRev: Building a dataset for Scientific Paragraph Revision annotated with revision instruction}.
\textit{International Workshop on Writing Aids at the Crossroads of AI, Cognitive Science and NLP (WR-AI-CogS)}.
\label{jourdan-etal-2025-pararev}

\item 
Enrico Benedetti, Akiko Aizawa, Florian Boudin.
2024.
\href{https://aclanthology.org/2024.acl-srw.11.pdf}{Automatically Suggesting Diverse Example Sentences for L2 Japanese Learners Using Pre-Trained Language Models}.
\textit{Association for Computational Linguistics (ACL): Student Research Workshop}.
\label{benedetti-etal-2024-automatically}

\item 
Léane Jourdan, \textbf{Florian Boudin}, Nicolas Hernandez, Richard Dufour.
2023.
\href{https://ceur-ws.org/Vol-3617/paper-04.pdf}{Text revision in Scientific Writing Assistance: A Review}.
\textit{International Workshop on Bibliometric-enhanced Information Retrieval (BIR)}.
\label{jourdan-etal-2023-text}

\item 
Maël Houbre, \textbf{Florian Boudin}, Béatrice Daille.
2022.
\href{https://aclanthology.org/2022.louhi-1.6.pdf}{A large-scale dataset for biomedical keyphrase generation}.
\textit{International Workshop on Health Text Mining and Information Analysis (LOUHI)}.
\label{houbre-etal-2022-large}

\item 
Amir Hazem, Mérieme Bouhandi, \textbf{Florian Boudin}, Beatrice Daille.
2020.
\href{https://aclanthology.org/2020.computerm-1.13.pdf}{TermEval 2020: TALN-LS2N System for Automatic Term Extraction}.
\textit{6th International Workshop on Computational Terminology (CompuTerm)}.
\label{hazem-etal-2020-termeval}

\item 
\textbf{Florian Boudin}, Hugo Mougard and Damien Cram.
2016.
\href{https://aclanthology.org/W16-3917.pdf}{How Document Pre-processing affects Keyphrase Extraction Performance}.
\textit{Workshop on Noisy User-generated Text (WNUT)}.
\label{boudin-etal-2016-document}

\item 
\textbf{Florian Boudin}.
2015.
\href{https://aclanthology.org/W15-3605.pdf}{Reducing Over-generation Errors for Automatic Keyphrase Extraction using Integer Linear Programming}.
\textit{Workshop on Novel Computational Approaches to Keyphrase Extraction}.
\label{boudin-2015-reducing}

\item 
Emmanuel Morin, Amir Hazem, \textbf{Florian Boudin}, Elizaveta Loginova-Clouet.
2015.
\href{https://aclanthology.org/W15-3413.pdf}{LINA: Identifying Comparable Documents from Wikipedia}.
\textit{Eighth Workshop on Building and Using Comparable Corpora (BUCC)}.
\label{morin-etal-2015-lina}

\item 
Romain Deveaud, \textbf{Florian Boudin}.
2013.
\href{http://www.clef-initiative.eu/documents/71612/f20ff540-8fc7-476a-9c51-db20f8413cc6}{Effective Tweet Contextualization with Hashtags Performance Prediction and Multi-Document Summarization}.
\textit{INitiative for the Evaluation of XML Retrieval (INEX)}.
\label{deveaud-boudin-2013-effective}

\item 
Romain Deveaud, \textbf{Florian Boudin}.
2012.
\href{https://hal.science/hal-00755496/document}{LIA/LINA at the INEX 2012 Tweet Contextualization track}.
\textit{INitiative for the Evaluation of XML Retrieval (INEX)}.
\label{deveaud-boudin-2012-lia}

\item 
Romain Deveaud, \textbf{Florian Boudin}, Patrice Bellot.
2011.
\href{https://link.springer.com/chapter/10.1007/978-3-642-23577-1_10}{LIA at INEX 2010 Book Track}
\textit{INitiative for the Evaluation of XML Retrieval (INEX)}.
\label{deveaud-etal-2011-lia}

\item 
\textbf{Florian Boudin}, Jian-Yun Nie, Martin Dawes.
2010.
\href{https://dl.acm.org/doi/10.1145/1871871.1871882}{Deriving a test collection for clinical information retrieval from systematic reviews}.
\textit{Data and Text Mining in Biomedical Informatics (DTMBIO)}.
\label{boudin-etal-2010-deriving}

\item 
\textbf{Florian Boudin}, Marc El-Bèze, Juan-Manuel Torres-Moreno.
2008.
\href{https://www.nist.gov/tac/publications/2008/participant.papers/LIA.proceedings.pdf}{The LIA Update Summarization system at TAC-2008}.
\textit{Text Analysis Conference (TAC)}.
\label{boudin-etal-2008-lia}

\item 
\textbf{Florian Boudin}, Benoit Favre, Frederic Béchet, Marc El-Bèze, Laurent Gillard, Juan-Manuel Torres-Moreno.
2007.
\href{http://www-nlpir.nist.gov/projects/duc/pubs/2007papers/uavignon.ps}{The LIA-Thales summarization system at DUC-2007}.
\textit{Document Understanding Conference (DUC)}.
\label{boudin-etal-2007-lia}

\item 
Benoit Favre, Frederic Béchet, Patrice Bellot, \textbf{Florian Boudin}, Marc El-Beze, Laurent Gillard, Guy Lapalme, Juan-Manuel Torres-Moreno.
2006.
\href{http://www-nlpir.nist.gov/projects/duc/pubs/2006papers/LIA-Thales_Duc06_final.pdf}{The LIA-Thales summarization system at DUC-2006}.
\textit{Document Understanding Conference (DUC)}.
\label{favre-etal-2006-lia}